\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-05-30 paper/figures/example-stats.tex
words about simulated examples

\begin{floattable}
\begin{deluxetable}{cccccccc}
\caption{The scaling and convergence stats for each example. \label{tab:example-stats}}
\tablehead{\colhead{example} & \colhead{$N$} & \colhead{$J$} & \colhead{direct cost} & \colhead{\celerite\ cost} & \colhead{$D$} & \colhead{steps} & \colhead{effective samples}\\
&&& \colhead{ms} & \colhead{ms} &&&}
\startdata
1 & 200 & 1 & 2.85 & 0.26 & 3 & 80000 & 1737 \\
2 & 100 & 2 & 0.67 & 0.36 & 4 & 80000 & 1134 \\
3 & 6950 & 2 & 7351.71 & 1.46 & 4 & 176000 & 3606 \\
4 & 1440 & 8 & 828.93 & 2.74 & 9 & 640000 & 1443 \\
5 & 1000 & 2 & 82.73 & 0.94 & 13 & 640000 & 1141 \\
\enddata
\end{deluxetable}
\end{floattable}

>>>>

\begin{floattable}
\begin{deluxetable}{cccccccc}
\caption{The scaling and convergence stats for each example. \label{tab:example-stats}}
\tablehead{\colhead{example} & \colhead{$N$} & \colhead{$J$} & \colhead{direct cost} & \colhead{\celerite\ cost} & \colhead{$D$} & \colhead{model evaluations} & \colhead{effective samples}\\
&&& \colhead{ms} & \colhead{ms} &&&}
\startdata
1 & 200 & 1 & 2.85 & 0.26 & 3 & 80000 & 1737 \\
2 & 100 & 2 & 0.67 & 0.36 & 4 & 80000 & 1134 \\
3 & 6950 & 2 & 7351.71 & 1.46 & 4 & 176000 & 3606 \\
4 & 1440 & 8 & 828.93 & 2.74 & 9 & 640000 & 1443 \\
5 & 1000 & 2 & 82.73 & 0.94 & 13 & 640000 & 1141 \\
\enddata
\end{deluxetable}
\end{floattable}

### 2017-05-30 paper/ms.tex
words about simulated examples

\include{vc}
\include{figures/rotation/rotation}

@@

GPs are stochastic models consisting of a mean function
$\mu_\bvec{\theta}(\bvec{x})$ and a covariance, autocorrelation, or ``kernel''
function $k_\bvec{\alpha}(\bvec{x}_n,\,\bvec{x}_m)$ parameterized by
$\bvec{\theta}$ and $\bvec{\alpha}$ respectively.
Under this model, the log-likelihood of observing a dataset
\begin{eqnarray}
\bvec{y} = \left(\begin{array}{ccccc}
    y_1\quad && \cdots\quad && y_N
\end{array}\right)^\T
\end{eqnarray}
at coordinates
\begin{eqnarray}
X = \left(\begin{array}{ccccc}
    \bvec{x}_1\quad && \cdots\quad && \bvec{x}_N
\end{array}\right)^\T
\end{eqnarray}
is
\begin{eqnarray}\eqlabel{gp-likelihood}
\ln{p(\bvec{y}\,|\,{X,\,\bvec{\theta}},\,\bvec{\alpha})} =
    -\frac{1}{2} {\bvec{r}_\bvec{\theta}}^\T\,{K_\bvec{\alpha}}^{-1}\,
        \bvec{r}_\bvec{\theta}
    -\frac{1}{2}\ln\det K_\bvec{\alpha}
    - \frac{N}{2} \ln{(2\pi)}
\end{eqnarray}
where
\begin{eqnarray}
    \bvec{r}_\bvec{\theta} = \left(\begin{array}{ccccc}
    y_1 - \mu_\bvec{\theta}(\bvec{x}_1)\quad && \cdots\quad &&
    y_N - \mu_\bvec{\theta}(\bvec{x}_N)
\end{array}\right)^\T
\end{eqnarray}
is the vector of residuals and the elements of the covariance matrix $K$ are
given by $[K_\bvec{\alpha}]_{nm} = k_\bvec{\alpha}(\bvec{x}_n,\,\bvec{x}_m)$.
\eq{gp-likelihood} is the equation of an $N$-dimensional Gaussian and it can
be derived as the generalization of what we astronomers call ``$\chi^2$''
to include the effects of correlated noise.
The maximum likelihood values for the parameters $\bvec{\theta}$ and
$\bvec{\alpha}$ for a given dataset $(\bvec{y},\,X)$ can be found by
maximizing \eq{gp-likelihood} with respect to $\bvec{\theta}$ and
$\bvec{\alpha}$ using a non-linear optimization routine \citep{Nocedal:2006}.
Similarly, probabilistic constraints on $\bvec{\theta}$ and $\bvec{\alpha}$
can be obtained by multiplying the likelihood by a prior
$p(\bvec{\theta},\,\bvec{\alpha})$ and using a Markov Chain Monte Carlo (MCMC)
algorithm to sample the joint posterior probability density.

@@

To relate this physical picture to \celeriteterm, we consider the dynamics of a
stochastically-driven damped simple harmonic oscillator.
The differential equation for this system is
\begin{equation}
    \left[\frac{\dd^2}{\dd t^2} + \frac{\omega_0}{Q}\,\frac{\dd}{\dd t}
    + \omega_0^2\right]\, y(t) = \epsilon(t)
\end{equation}
where $\omega_0$ is the frequency of the undamped oscillator, $Q$ is the
quality factor of the oscillator, and $\epsilon(t)$ is a stochastic driving
force.
If $\epsilon(t)$ is white noise, the PSD of this process is
\citep{Anderson:1990}
\begin{equation}\eqlabel{sho-psd}
S(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{S_0\,\omega_0^4}
    {(\omega^2-\omega_0^2)^2 + \omega_0^2\omega^2/Q^2}
\end{equation}
where $S_0$ is proportional to the power at $\omega = \omega_0$, $S(\omega_0)
= \sqrt{2/\pi}\,S_0\,Q^2$.
The power spectrum in \eq{sho-psd} matches \eq{celerite-psd} if
\begin{eqnarray}\eqlabel{sho-complex}
a_j &=& S_0\,\omega_0\,Q \\
b_j &=& \frac{S_0\,\omega_0\,Q}{\sqrt{4\,Q^2-1}} \\
c_j &=& \frac{\omega_0}{2\,Q}\\
d_j &=& \frac{\omega_0}{2\,Q} \sqrt{4\,Q^2-1} \quad,
\end{eqnarray}
for $Q \ge \frac{1}{2}$.
For $0 < Q \le \frac{1}{2}$, \eq{sho-psd} can be captured by a pair of
\celeriteterm\
terms with parameters
\begin{eqnarray}\eqlabel{sho-real}
a_{j\pm} &=& \frac{1}{2}\,S_0\,\omega_0\,Q\,\left[ 1 \pm
        \frac{1}{\sqrt{1-4\,Q^2}}\right] \\
b_{j\pm} &=& 0 \nonumber\\
    c_{j\pm} &=& \frac{\omega_0}{2\,Q}\,\left[1 \mp \sqrt{1-4\,Q^2}\right]
    \nonumber\\
d_{j\pm} &=& 0 \quad. \nonumber
\end{eqnarray}

For these definitions, the kernel is
\begin{equation}\eqlabel{sho-kernel}
k(\tau) = S_0\,\omega_0\,Q\,e^{-\frac{\omega_0\,\tau}{2Q}}\,
\begin{cases}
    \cosh{(\eta\,\omega_0\,\tau)} +
        \frac{1}{2\,\eta\,Q}\,\sinh{(\eta\,\omega_0\,\tau)}, & 0 < Q < 1/2\\
    2\,(1+\omega_0\,\tau), & Q = 1/2\\
    \cos{(\eta\,\omega_0\,\tau)} +
        \frac{1}{2\,\eta\,Q} \sin{(\eta\,\omega_0\,\tau)},& 1/2 < Q\\
\end{cases}
\end{equation}
where $\eta = \vert 1-(4\,Q^2)^{-1}\vert^{1/2}$.
We note that, because of the damping, the characteristic oscillation frequency
in this model, $d_j$, for any finite quality factor $Q > 1/2$, is not equal to
the frequency of the undamped oscillator, $\omega_0$.

@@

@@

In this first example, we simulate a dataset using a known \celeriteterm\
process and fit it with \celerite\ to demonstrate that valid inferences can be
made in this idealized case.
The simulated dataset is shown in the left panel of \Figure{simulated-correct}
and it was generated using a SHO kernel (\eqalt{sho-kernel}) with parameters
$S_0 = 1$, $\omega_0 = e^2$, and $Q = e^2$.
The true PSD is shown as a dashed line in the right panel of
\Figure{simulated-correct}.
We applied log-uniform priors to all of the parameters and used \emcee\
\citep{Foreman-Mackey:2013} to sample the joint posterior density and computed
the marginalized posterior inference of the PSD.
This inference is shown in the right panel of \Figure{simulated-correct} as a
blue contour indicating 68\% of the posterior mass.
It is clear from this figure that, as expected, the inference correctly
reproduces the true PSD.

@@

For this example, we simulate a dataset using a known GP model with a kernel
outside of the support of a \celeriteterm\ process.
This means the true autocorrelation of the process can never be correctly
represented by the model that we are using to fit, but we use this example
to demonstrate that, at least in this case, valid inferences can still be made
about the physical parameters of the model.

For this example, the data are simulated from a quasiperiodic GP with the
kernel
\begin{eqnarray}\eqlabel{sim-wrong-true}
k_\mathrm{true} (\tau) = \alpha\,
    \exp\left(-\frac{\tau^2}{2\,\lambda^2}\right)\,
    \cos\left(\frac{2\,\pi\,\tau}{P_\mathrm{true}}\right)
\end{eqnarray}
where $P_\mathrm{true}$ is the fundamental period of the process.
This autocorrelation structure corresponds to the power spectrum
\begin{eqnarray}
S_\mathrm{true} (\omega) = \frac{\lambda\,\alpha}{2}\,\left[
    \exp\left(-\frac{\lambda^2}{2}\,\left(\omega-
        \frac{2\,\pi}{P_\mathrm{true}}\right)^2\right) +
    \exp\left(-\frac{\lambda^2}{2}\,\left(\omega+
        \frac{2\,\pi}{P_\mathrm{true}}\right)^2\right)
\right]
\end{eqnarray}
which, for large values of $\omega$, falls off exponentially.
When compared to \eq{celerite-psd}~--~which, for large $\omega$, goes as
$\omega^{-4}$ at most~--~it is clear that a \celeriteterm\ model can never
perfectly reproduce the structure of this process.
That being said, we demonstrate that rigorous inferences can be made
about $P_\mathrm{true}$ even with an effective model.
The left panel of \Figure{simulated-wrong} shows the simulated dataset.
We then fit this simulated data using the product of two SHO terms
(\eqalt{sho-kernel}) where one of the terms has $S_0 = 1$ and $Q =
1/\sqrt{2}$ and the other has $\omega_0 = 2\,\pi/P$.
We note that using \eq{product-rule}, the product of two \celeriteterm\ terms can
also be expressed using \celerite.
We apply log-uniform priors on all the parameters and use \emcee\ to sample
the joint posterior probability for all of the parameters.
The inferred distribution for the parameter $P$ is shown in the right panel of
\Figure{simulated-wrong} and compared to the true period $P_\mathrm{true}$ and
the inferences made using the correct model (\eqalt{sim-wrong-true}).
The inference made using this effective \celeriteterm\ model are indistinguishable
from the inferences made using the correct model and substantially less
computation time is required for the \celerite\ inference.

>>>>

\include{vc}
\include{figures/examples-macros}
\include{figures/rotation/rotation}

@@

GPs are stochastic models consisting of a mean function
$\mu_\bvec{\theta}(\bvec{x})$ and a covariance, autocorrelation, or ``kernel''
function $k_\bvec{\alpha}(\bvec{x}_n,\,\bvec{x}_m)$ parameterized by
$\bvec{\theta}$ and $\bvec{\alpha}$ respectively.
Under this model, \response{the log-likelihood function $\mathcal{L}
(\bvec{\theta},\,\bvec{\alpha})$} with a dataset
\begin{eqnarray}
\bvec{y} = \left(\begin{array}{ccccc}
    y_1\quad && \cdots\quad && y_N
\end{array}\right)^\T
\end{eqnarray}
at coordinates
\begin{eqnarray}
X = \left(\begin{array}{ccccc}
    \bvec{x}_1\quad && \cdots\quad && \bvec{x}_N
\end{array}\right)^\T
\end{eqnarray}
is
\begin{eqnarray}\eqlabel{gp-likelihood}
\ln \mathcal{L} (\bvec{\theta},\,\bvec{\alpha}) =
\ln{p(\bvec{y}\,|\,{X,\,\bvec{\theta}},\,\bvec{\alpha})} =
    -\frac{1}{2} {\bvec{r}_\bvec{\theta}}^\T\,{K_\bvec{\alpha}}^{-1}\,
        \bvec{r}_\bvec{\theta}
    -\frac{1}{2}\ln\det K_\bvec{\alpha}
    - \frac{N}{2} \ln{(2\pi)}
\end{eqnarray}
where
\begin{eqnarray}
    \bvec{r}_\bvec{\theta} = \left(\begin{array}{ccccc}
    y_1 - \mu_\bvec{\theta}(\bvec{x}_1)\quad && \cdots\quad &&
    y_N - \mu_\bvec{\theta}(\bvec{x}_N)
\end{array}\right)^\T
\end{eqnarray}
is the vector of residuals and the elements of the covariance matrix $K$ are
given by $[K_\bvec{\alpha}]_{nm} = k_\bvec{\alpha}(\bvec{x}_n,\,\bvec{x}_m)$.
\eq{gp-likelihood} is the equation of an $N$-dimensional Gaussian and it can
be derived as the generalization of what we astronomers call ``$\chi^2$''
to include the effects of correlated noise.
The maximum likelihood values for the parameters $\bvec{\theta}$ and
$\bvec{\alpha}$ for a given dataset $(\bvec{y},\,X)$ can be found by
maximizing \eq{gp-likelihood} with respect to $\bvec{\theta}$ and
$\bvec{\alpha}$ using a non-linear optimization routine \citep{Nocedal:2006}.
Similarly, probabilistic constraints on $\bvec{\theta}$ and $\bvec{\alpha}$
can be obtained by multiplying the likelihood by a prior
$p(\bvec{\theta},\,\bvec{\alpha})$ and using a Markov Chain Monte Carlo (MCMC)
algorithm to sample the joint posterior probability density.

@@

To relate this physical picture to \celeriteterm, we consider the dynamics of a
stochastically-driven damped simple harmonic oscillator (SHO).
The differential equation for this system is
\begin{equation}
    \left[\frac{\dd^2}{\dd t^2} + \frac{\omega_0}{Q}\,\frac{\dd}{\dd t}
    + \omega_0^2\right]\, y(t) = \epsilon(t)
\end{equation}
where $\omega_0$ is the frequency of the undamped oscillator, $Q$ is the
quality factor of the oscillator, and $\epsilon(t)$ is a stochastic driving
force.
If $\epsilon(t)$ is white noise, the PSD of this process is
\citep{Anderson:1990}
\begin{equation}\eqlabel{sho-psd}
S(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{S_0\,\omega_0^4}
    {(\omega^2-\omega_0^2)^2 + \omega_0^2\omega^2/Q^2}
\end{equation}
where $S_0$ is proportional to the power at $\omega = \omega_0$, $S(\omega_0)
= \sqrt{2/\pi}\,S_0\,Q^2$.
The power spectrum in \eq{sho-psd} matches \eq{celerite-psd} if
\begin{eqnarray}\eqlabel{sho-complex}
a_j &=& S_0\,\omega_0\,Q \\
b_j &=& \frac{S_0\,\omega_0\,Q}{\sqrt{4\,Q^2-1}} \\
c_j &=& \frac{\omega_0}{2\,Q}\\
d_j &=& \frac{\omega_0}{2\,Q} \sqrt{4\,Q^2-1} \quad,
\end{eqnarray}
for $Q \ge \frac{1}{2}$.
For $0 < Q \le \frac{1}{2}$, \eq{sho-psd} can be captured by a pair of
\celeriteterm\
terms with parameters
\begin{eqnarray}\eqlabel{sho-real}
a_{j\pm} &=& \frac{1}{2}\,S_0\,\omega_0\,Q\,\left[ 1 \pm
        \frac{1}{\sqrt{1-4\,Q^2}}\right] \\
b_{j\pm} &=& 0 \nonumber\\
    c_{j\pm} &=& \frac{\omega_0}{2\,Q}\,\left[1 \mp \sqrt{1-4\,Q^2}\right]
    \nonumber\\
d_{j\pm} &=& 0 \quad. \nonumber
\end{eqnarray}

For these definitions, the kernel is
\begin{equation}\eqlabel{sho-kernel}
k_\mathrm{SHO}(\tau;\,S_0,\,Q,\,\omega_0) =
S_0\,\omega_0\,Q\,e^{-\frac{\omega_0\,\tau}{2Q}}\,
\begin{cases}
    \cosh{(\eta\,\omega_0\,\tau)} +
        \frac{1}{2\,\eta\,Q}\,\sinh{(\eta\,\omega_0\,\tau)}, & 0 < Q < 1/2\\
    2\,(1+\omega_0\,\tau), & Q = 1/2\\
    \cos{(\eta\,\omega_0\,\tau)} +
        \frac{1}{2\,\eta\,Q} \sin{(\eta\,\omega_0\,\tau)},& 1/2 < Q\\
\end{cases}
\end{equation}
where $\eta = \vert 1-(4\,Q^2)^{-1}\vert^{1/2}$.
We note that, because of the damping, the characteristic oscillation frequency
in this model, $d_j$, for any finite quality factor $Q > 1/2$, is not equal to
the frequency of the undamped oscillator, $\omega_0$.

@@

\response{In each example, the joint posterior probability density is given by
\begin{eqnarray}\eqlabel{joint-post}
p(\bvec{\theta},\,\bvec{\alpha}\,|\,\bvec{y},\,X) \propto
p(\bvec{y}\,|\,{X,\,\bvec{\theta}},\,\bvec{\alpha})\,
p(\bvec{\theta},\,\bvec{\alpha})
\end{eqnarray}
where $p(\bvec{y}\,|\,{X,\,\bvec{\theta}},\,\bvec{\alpha})$ is the GP
likelihood defined in \eq{gp-likelihood} and
$p(\bvec{\theta},\,\bvec{\alpha})$ is the joint prior probability density for
the parameters.
The specific parameters and priors are discussed in detail in each section
but, in most cases, we assume separable uniform priors with plausibly broad
support.
}

@@

In this first example, we simulate a dataset using a known \celeriteterm\
process and fit it with \celerite\ to demonstrate that valid inferences can be
made in this idealized case.
\response{We simulated a small ($N = \exampleindata$) dataset using a GP model
with a SHO kernel (\eqalt{sho-kernel}) with parameters $S_0 =
1\,\mathrm{ppm}^2$, $\omega_0 = e^2\,\mathrm{day}^{-1}$, and $Q = e^2$, where
the units are arbitrarily chosen to simplify the discussion.
We add further white noise with the amplitude $\sigma_n = 2.5\, \mathrm{ppm}$
to each data point.
The simulated data are plotted in the top left panel of
\Figure{simulated-correct}.

In this case, when simulating and fitting, we set the mean function
$\mu_\bvec{\theta}$ to zero~--~this means that the parameter vector
$\bvec{\theta}$ is empty~--~and the elements of the covariance matrix are
given by \eq{sho-kernel} with three parameters $\bvec{\alpha} = (S_0,\,
\omega_0,\,Q)$.
We choose a proper separable prior for $\bvec{\alpha}$ with log-uniform
densities for each parameter as listed in Table~\ref{tab:example-1-params}.

To start, we estimate the maximum \emph{a posteriori} (MAP) parameters using
the \project{L-BFGS-B} non-linear optimization routine \citep{Byrd:1995,
Zhu:1997} implemented by the \project{SciPy} project \citep{Jones:2001}.
The top left panel of \Figure{simulated-correct} shows the conditional mean
and standard deviation of the MAP model over-plotted on the simulated data and
the bottom panel shows the residuals away from this model.
Since we are using the correct model to fit the data, it is reassuring that
the residuals appear qualitatively uncorrelated in this figure.

We then sample the joint posterior probability (\eqalt{joint-post}) using
\emcee\ \citep{Goodman:2010, Foreman-Mackey:2013}.
We initialize \exampleinwalkers~walkers in a Gaussian ball with width
$10^{-4}$ in each parameter around the MAP parameter vector, run
\exampleinburn~steps of burn-in, and \exampleinsteps~steps of MCMC.
To asses convergence, we estimate the mean integrated autocorrelation time of
the chain across parameters \citep{Sokal:1989, Goodman:2010} and find that the
chain results in \exampleineff~effective samples.

Each sample in the chain corresponds to a model PSD and we compare this
posterior constraint on the PSD to the true spectral density in the
right-hand panel of \Figure{simulated-correct}.
In this figure, the true PSD is plotted as a dashed black line and the
numerical estimate of the posterior inference is shown as a blue contour
indicating 68\% of the MCMC samples.
It is clear from this figure that, as expected, the inference correctly
reproduces the true PSD.
}

@@

In this example, we simulate a dataset using a known GP model with a kernel
outside of the support of a \celeriteterm\ process.
This means the true autocorrelation of the process can never be correctly
represented by the model that we are using to fit, but we use this example
to demonstrate that, at least in this case, valid inferences can still be made
about the physical parameters of the model.

The data are simulated from a quasiperiodic GP with the kernel
\begin{eqnarray}\eqlabel{sim-wrong-true}
k_\mathrm{true} (\tau) = \alpha\,
    \exp\left(-\frac{\tau^2}{2\,\lambda^2}\right)\,
    \cos\left(\frac{2\,\pi\,\tau}{P_\mathrm{true}}\right)
\end{eqnarray}
where $P_\mathrm{true}$ is the fundamental period of the process.
This autocorrelation structure corresponds to the power spectrum
\citep{Wilson:2013}
\begin{eqnarray}
S_\mathrm{true} (\omega) = \frac{\lambda\,\alpha}{2}\,\left[
    \exp\left(-\frac{\lambda^2}{2}\,\left(\omega-
        \frac{2\,\pi}{P_\mathrm{true}}\right)^2\right) +
    \exp\left(-\frac{\lambda^2}{2}\,\left(\omega+
        \frac{2\,\pi}{P_\mathrm{true}}\right)^2\right)
\right]
\end{eqnarray}
which, for large values of $\omega$, falls off exponentially.
When compared to \eq{celerite-psd}~--~which, for large $\omega$, goes as
$\omega^{-4}$ at most~--~it is clear that a \celeriteterm\ model can never
exactly reproduce the structure of this process.
That being said, we demonstrate that robust inferences can be made about
$P_\mathrm{true}$ even with this effective model.

\response{We generate a realization of a GP model with the kernel given in
\eq{sim-wrong-true} with $N = \exampleiindata$, $\alpha = 1\,\mathrm{ppm}^2$,
$\lambda = 5\,\mathrm{day}$, and $P_\mathrm{true} = 1\,\mathrm{day}$.
We also add white noise with amplitude $\sigma = 0.5\,\mathrm{ppm}$ to each
data point.
The top left panel of \Figure{simulated-wrong} shows this simulated dataset.

We then fit this simulated data using the product of two SHO terms
(\eqalt{sho-kernel}) where one of the terms has $S_0 = 1$ and $Q =
1/\sqrt{2}$ fixed.
The kernel for this model is
\begin{eqnarray}
k(\tau) = k_\mathrm{SHO}(\tau;\,S_0,\,Q,\,\omega_1) \,
    k_\mathrm{SHO}(\tau;\,S_0 = 1,\,Q = 1/\sqrt{2},\,\omega_2)
\end{eqnarray}
where $k_\mathrm{SHO}$ is defined in \eq{sho-kernel} and the inferred period
is related to the parameters by $P=2\,\pi/\omega_1$.
We note that using \eq{product-rule}, the product of two \celeriteterm\ terms
can also be expressed using \celerite.

As in the previous example, we set the mean function to zero and can,
therefore, omit the parameters $\bvec{\theta}$.
Table~\ref{tab:example-2-params} lists the proper log-uniform priors that we
choose for each parameter in $\bvec{\alpha} =
(S_0,\,Q,\,\omega_1,\,\omega_2)$.
These priors, together with the GP likelihood (\eqalt{gp-likelihood}) fully
specify the posterior probability density.

As above, we estimate the MAP parameters using \project{L-BFGS-B} and sample
the posterior probability density using \emcee.
The top left panel of \Figure{simulated-wrong} shows the conditional mean and
standard deviation of the MAP model.
The bottom left panel shows the residuals between the data and this MAP model
and, even though this GP model is formally ``wrong'', there are no obvious
correlations in these residuals.

To perform posterior inference, we initialize \exampleiinwalkers~walkers by
sampling from the 4-dimensional Gaussian centered on the MAP parameters with
an isotropic standard deviation of $10^{-4}$.
We then run \exampleiinburn~steps of burn-in and \exampleiinsteps~steps of
MCMC.
To estimate the number of effective samples, we estimate the integrated
autocorrelation time of the chain for the parameter $\omega_1$~--~the
parameter of primary interest~--~and find \exampleiineff~effective samples.

For comparison, we run the same number of steps of MCMC to sample the
``correct'' joint posterior density.
For this reference inference, we use a GP likelihood with the kernel given by
\eq{sim-wrong-true} and choose log-uniform priors on each of the
three parameters $\ln \alpha/\mathrm{ppm}^2 \sim \mathcal{U}(-10,\,10)$,
$\ln \lambda/\mathrm{day} \sim \mathcal{U}(-10,\,10)$, and
$\ln P_\mathrm{true}/\mathrm{day} \sim \mathcal{U}(-10,\,10)$.

The marginalized posterior inferences of the characteristic period of the
process are shown in the right panel of \Figure{simulated-wrong}.
The inference using the correct model is shown as a dashed blue histogram and
the inference made using the effective model is shown as a solid black
histogram.
These inferences are consistent with each other and with the true period used
for the simulation (shown as a vertical gray line).
This demonstrates that, in this case, \celerite\ can be used as a
computationally efficient effective model and hints that this may be true in
other problems as well.
}
